TITLE

### 2021-02-25 outputs/Paper.Rmd
update

* `type` : Unique row identifier for Open Data database
* `Q1` : Unique row identifier for Open Data database
* `Q2` : Unique row identifier for Open Data database
* `Q3` : Unique row identifier for Open Data database
* `Q4` : Unique row identifier for Open Data database
* `Q5` : Unique row identifier for Open Data database
* `Q6` : Unique row identifier for Open Data database
* `Q7` : Unique row identifier for Open Data database
* `Q8` : Unique row identifier for Open Data database
* `Q9` : Unique row identifier for Open Data database
* `Q10` : Unique row identifier for Open Data database
* `Q11` : Unique row identifier for Open Data database
* `Q12` : Unique row identifier for Open Data database
* `Q13` : Unique row identifier for Open Data database
* `Q14` : Unique row identifier for Open Data database

>>>>

* `type` : Categorical identifier [“Treated” or “Control”] for each observation 
* `Q1` : First three digitals of the postcode 
* `Q2` : Categorical identifier for distinguishing the type of restaurants 
* `Q3` : Region name in GTA
* `Q4` : Describe whether the restaurant is a franchise (“Franchise” or “No”)
* `Q5` : The length of the operation years for each restaurant 
* `Q6` : Describe whether the restaurant offer takeout service (“Yes” or “No”)
* `Q7` : Describe whether the restaurant offer delivery service (“Yes” or “No”)
* `Q8` : Number of employees in the restaurant (category type)
* `Q9` : Average employee hourly rate (CAD) 
* `Q10` : Describe whether the restaurant has been a site of a potential COVID case (“Yes” or “No”)
* `Q11` : Describe the restaurant’s fixed costs change situation 
* `Q12` :  Describe the restaurant’s flexible costs change situation 
* `Q13` : The restaurant’s past month revenue (CAD)

The first six rows of raw data is shown in the table1 below. (Table \@ref(tab:rowdata))
```{r rowdata, echo=FALSE}
#plot row data set in table
  head(simulated_data)%>%
  select(-size)%>%
  kableExtra::kbl(caption = "First 6 rows Raw data ") %>%
  kableExtra::kable_styling(latex_options = "scale_down") # use scale_down option to make the font
```
